Using traffic analysis to identify The Second Generation Onion Router

### 2011-08-11 ieee-conference-paper/paper.tex
Even larger histograms, spread out a bit throughout the paper
Add a little bit more prior research

When considering the use of traffic analysis for classification of Internet
communications, three techniques are used: exact matching, heuristic matching
and machine learning \parencite{Zhang:2009p1188}.

@@

\begin{figure*}
  \centering\includegraphics[width=0.6\linewidth]{https_hist}
  \caption{Histogram of packet size for HTTPS traffic}
  \label{https_hist}
\end{figure*}

\begin{figure*}
  \centering\includegraphics[width=0.6\linewidth]{http_tor_hist}
  \caption{Histogram of packet size for HTTP traffic over Tor}
  \label{http_tor_hist}
\end{figure*}

\begin{figure*}
  \centering\includegraphics[width=0.6\linewidth]{https_tor_hist}
  \caption{Histogram of packet size for HTTPS traffic over Tor}
  \label{https_tor_hist}
\end{figure*}

@@

This knowledge can be used to build a rudimentary classification algorithm to
identify Tor traffic, the pseudo code for an example algorithm is included in
Figure \ref{psuedo_matcher}. Applying this algorithm to the complete traces
yields the results as seen in Table \ref{table:heuristic-results}.

@@

\begin{figure}
  \begin{lstlisting}[language=ruby]
    if  packet[3] > 130 and
        packet[3] <  153 and
        packet[5] > 913 and
        packet[5] < 937 then
      is_tor = true
    else
      is_tor = false
    end
  \end{lstlisting}
  \caption{Pseudo Code for Matching a Tor Session}
  \label{psuedo_matcher}
\end{figure}

>>>>

When considering the use of traffic analysis for classification of Internet
communications, three techniques are used: exact matching, heuristic matching
and machine learning \parencite{Zhang:2009p1188}. Since Tor employs strong
encryption and can communicate on any port, it can easily an exact matching
technique through simple configuration options.

Heuristic based techniques have been designed to classify encrypted
communications, including the identification of P2P traffic
\parencite{Karagiannis:2004p6400,Perenyi:2006p6325,John:2008p1376} and viruses
\parencite{Lazarevic:2003p6450}.

Machine learning algorithms have also been used successfully to classify
encrypted traffic including Skype \parencite{Alshammari:2009p7474} and to
identify application protocols tunnelled over SSH \parencite{Dusi:2008p6254}.
An previous attempt to classify Tor using Bayesian networks was attempted in
\textcite{Herrmann:2009p1189} without great success.

@@

\begin{figure*}
  \centering\includegraphics[width=0.9\linewidth]{https_hist}
  \caption{Histogram of packet size for HTTPS traffic}
  \label{https_hist}
\end{figure*}

\begin{figure*}
  \centering\includegraphics[width=0.9\linewidth]{http_tor_hist}
  \caption{Histogram of packet size for HTTP traffic over Tor}
  \label{http_tor_hist}
\end{figure*}

\begin{figure*}
  \centering\includegraphics[width=0.9\linewidth]{https_tor_hist}
  \caption{Histogram of packet size for HTTPS traffic over Tor}
  \label{https_tor_hist}
\end{figure*}

@@

This knowledge can be used to build a rudimentary classification algorithm to
identify Tor traffic, the pseudo code for an example algorithm is included in
Figure \ref{psuedo_matcher}.

\begin{figure}[H]
  \begin{lstlisting}[language=ruby]
    if  packet[3] > 130 and
        packet[3] < 153 and
        packet[5] > 913 and
        packet[5] < 937 then
      is_tor = true
    else
      is_tor = false
    end
  \end{lstlisting}
  \caption{Pseudo Code for Matching a Tor Session}
  \label{psuedo_matcher}
\end{figure}

Applying this algorithm to the complete traces
yields the results as seen in Table \ref{table:heuristic-results}.

@@
